Price of Anarchy for Mean Field Games

### 2018-08-01 PoA.tex
almost finished with lemma 1
minor edits, condensing lemma 1

	First, we show that for $t\in[0,T)$: (ToDo: This is already stated in Proposition 4.)

@@

	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$:
	$$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$$

@@

	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for any $b_2$, the function $t \mapsto b_2 \eta^{b_2}_t$ is continuous, by the intermediate value theorem we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, there exists a $t^*_{b_2}\in[0,T]$ such that:
	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$$
	and:
	$$b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
	Thus,
	$$1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta=\frac{\frac{1}{b_2} \left[ToDO \right]}{\frac{1}{b_2^2} \left[ToDo \right]}-c_\eta=\frac{ToDo}{ToDo}.$$
	After rearranging terms:

@@

	\frac{D}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)} \\
	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)}.

@@

	Since we have: (ToDo: show these limits)
	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$$
	there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$

@@

	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$

@@

	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).

@@

	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{\delta^{+,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, $$
	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2},$$
	and thus,
	$$c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	

@@

	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$

@@

	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	

>>>>

	As noted in the proof of Proposition \ref{prop:b2_to_infty}, for $t\in[0,T)$, we have:

@@

	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have
	$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$

@@

	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing. Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that:
	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1, \quad \text{and} \quad b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
	Thus for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, we have:
	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,
	$$
	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},
	$$

@@

	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
	&= \left[-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
	&\leq  \left[-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.

@@

	It is easy to derive the following limits:
	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0.$$
	Therefore, there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$

@@

	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$

@@

	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).

@@

	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, \quad \text{and} \quad c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	

@@

	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(5c_\eta+2 \right).$$

@@

	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M.	
